Parsing Postfix log files

### 2009-03-06 doc/logparser-acronyms.tex
Dealt with some XXX items.

\newglossaryentry{SMTP}{
    type=\acronymtype,
    name={SMTP},
    description={Simple Mail Transfer Protocol},
    first={Simple Mail Transfer Protocol (SMTP)}
}
\newcommand{\SMTPglossaryDescription}[0]{%
    \acronym{SMTP} is the protocol used for transferring mail between the
    sending and receiving \acronym{MTA}\@.  It is a simple, human readable,
    plain text protocol, making it quite simple to test and debug problems
    with it.  A detailed description of SMTP is beyond the scope of this
    thesis: the original protocol definition is in RFC~821~\cite{RFC821},
    updated in RFC~2821~\cite{RFC2821}; introductory guides can be found at
    \urlLastChecked{http://db.glug-bom.org/lug-authors/philip/docs/mail-stuff/smtp-intro.html}{2009/02/28}
    if more information is needed.%
}
\newglossaryentry{SMTP glossary}{
    name={Simple Mail Transfer Protocol},
    description={
        \SMTPglossaryDescription{}
    }
}

>>>>

\newglossaryentry{SMTP}{
    type=\acronymtype,
    name={SMTP},
    description={Simple Mail Transfer Protocol},
    first={Simple Mail Transfer Protocol (SMTP)}
}
\newcommand{\SMTPglossaryDescription}[0]{%
    \acronym{SMTP} is the protocol used for transferring mail between the
    sending and receiving \acronym{MTA}\@.  It is a simple, human readable,
    plain text protocol, making it quite simple to test and debug problems
    with it.  A detailed description of SMTP is beyond the scope of this
    thesis: the original protocol definition is in RFC~821~\cite{RFC821},
    updated in RFC~2821~\cite{RFC2821}; an introductory guide can be found
    at
    \urlLastChecked{http://db.glug-bom.org/lug-authors/philip/docs/mail-stuff/smtp-intro.html}{2009/02/28}
    if more information is needed.%
}
\newglossaryentry{SMTP glossary}{
    name={Simple Mail Transfer Protocol},
    description={
        \SMTPglossaryDescription{}
    }
}

### 2009-03-06 doc/logparser-architecture.tex
Dealt with some XXX items.

The architecture can be thought of as implementing transduction: it takes
data in one form and transforms it to another form; \parsername{}
transforms log files to a database.  XXX NEED A REFERENCE FOR
TRANSDUCTION\@.

@@

Conditions can also check the value of variables that have been set by
either actions or rules; it is easier to understand how a variable's value
will be used and changed if it is set by rules only rather than by actions,
because the chain of checking and setting can be followed from rule to
rule.  The downside to actions setting variables used in rule conditions is
action at a distance: understanding when a rule's condition will be true or
false requires understanding not just every other rule but also every
action.  The framework probably does not need to support a high level of
complexity and flexibility when rules are setting variables; however, if
the framework supports complex conditions, that code can probably be easily
extended to support complex variable assignments too.  The level of
complexity the framework supports when evaluating conditions and setting
variables has two costs that must be taken into account when designing a
parser: the difficulty of implementation, and the difficulty of
understanding rules and writing correct rules.  XXX NEEDS TO BE IMPROVED\@.

@@

\begin{table}[ht]
    \caption{Rules to parse C-style comments}
    \empty{}\label{Rules to parse C-style comments}
    \begin{tabular}{llll}
        \tabletopline{}%
        No.   & Regex             & Condition           & Variable Changes    \\
        \tablemiddleline{}%
        % XXX WHAT SHOULD THE VARIABLE BE CALLED?
        1     & \verb!/\*.*?\*/!  & parsing == code     & parsing = code      \\
        2     & \verb!/\*.*!      & parsing == code     & parsing = comment   \\
        3     & \verb!.*\*/!      & parsing == comment  & parsing = code      \\
        4     & \verb!.*!         & parsing == comment  & parsing = comment   \\
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@

XXX IS THERE ANY PREVIOUS RESEARCH IN THIS AREA\@?

@@

Once conditions pass a certain level of complexity determining whether two
conditions overlap becomes intractable, because it requires so much
knowledge of other rules and possibly even actions.  E.g.\ given two rules
with conditions \verb!verbose == true! and \verb!silent == true!, logically
these rules should not overlap, yet there is nothing to stop both variables
being set to true by one or more rules or actions.  If variables used in
conditions can be set by actions, determining whether two conditions
overlap is impossible, because understanding how an action will change the
variables is impossible.  XXX DO I NEED TO MENTION CHURCH-TURING OR
ANYTHING\@?

>>>>

The architecture can be thought of as implementing transduction: it takes
data in one form and transforms it to another form; \parsername{}
transforms log files to a database.

@@

Conditions can also check the value of variables that have been set by
either actions or rules; it is easier to understand how a variable's value
will be used and changed if it is set by rules only rather than by actions,
because the chain of checking and setting can be followed from rule to
rule.  The downside to actions setting variables used in rule conditions is
action at a distance: understanding when a rule's condition will be true or
false requires understanding not just every other rule but also every
action.  The framework probably does not need to support a high level of
complexity and flexibility when rules are setting variables; however, if
the framework supports complex conditions, that code can probably be easily
extended to support complex variable assignments too.  The level of
complexity the framework supports when evaluating conditions and setting
variables has two costs that must be taken into account when designing a
parser: the difficulty of implementation, and the difficulty of
understanding writing correct rules; the flexibility provided by complex
conditions may be outweighed by the difficulty in understanding the
interactions between rules that use complex conditions.

@@

\begin{table}[ht]
    \caption{Rules to parse C-style comments}
    \empty{}\label{Rules to parse C-style comments}
    \begin{tabular}{llll}
        \tabletopline{}%
        No.   & Regex             & Condition             & Variable Changes    \\
        \tablemiddleline{}%
        1     & \verb!/\*.*?\*/!  & expecting == code     & expecting = code      \\
        2     & \verb!/\*.*!      & expecting == code     & expecting = comment   \\
        3     & \verb!.*\*/!      & expecting == comment  & expecting = code      \\
        4     & \verb!.*!         & expecting == comment  & expecting = comment   \\
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@

@@

Once conditions pass a certain level of complexity determining whether two
conditions overlap becomes intractable, because it requires so much
knowledge of other rules and possibly even actions.  E.g.\ given two rules
with conditions \verb!verbose == true! and \verb!silent == true!, logically
these rules should not overlap, yet there is nothing to stop both variables
being set to true by one or more rules or actions.  If variables used in
conditions can be set by actions, determining whether or not two conditions
overlap is impossible: the Halting Problem show that it is impossible for
one program to answer questions about another program's behaviour if the
inquiring program is implemented on a compuational machine of the equal or
lesser power to the program being inquired into.

### 2009-03-06 doc/logparser.tex
Corrections to second half of architecture chapter.
Dealt with some XXX items.

% Add last checked dates to all URLs
\newcommand{\urlLastChecked}[3][ ]{%
    \url{#2}#1(last checked #3)%
}
\newcommand{\daemonDocURL}[3][]{%
    \hfill{} \newline{} \url{#2}%
    \hfill{} #1 Last checked #3%
}
% XXX CAN I MAKE THIS LOOK BETTER?  MAYBE USE [] LIKE \pageref{} DOES?
\newcommand{\urlLastCheckedNoParens}[3][ ]{%
    \url{#2}#1last checked #3%
}

@@

\newcommand{\numberOFruleINTERSECTIONS}[0]{%
    17020%
}

@@

XXX ASK CARL ABOUT\@:

\begin{itemize}

    \item XXX WHERE SHOULD I USE URLS AND WHERE SHOULD THEY BE BIBLIOGRAPHY
        ENTRIES\@?

    \item XXX REFERENCE FOR TRANSDUCTION\@.

    \item XXX PREVIOUS RESEARCH IN OVERLAPPING RULES\@?

    \item XXX BORROW SPINNING WHEEL BOOK\@; NEED TO COMMENT ON THE
        COMPUTATIONAL COMPLEXITY OF FA UNION AND INVERSION\@; MAYBE COMMENT
        ON COMPUTATIONAL COMPLEXITY OF PDA UNION, INVERSION, AND
        INTERSECTION\@?

    \item XXX BIB ENTRY FOR CHURCH-TURING\@.

\end{itemize}

>>>>

% Add last checked dates to all URLs
\newcommand{\urlLastChecked}[3][ ]{%
    \url{#2}#1(last checked #3)%
}
\newcommand{\daemonDocURL}[3][]{%
    \hfill{} \newline{} \url{#2}%
    \hfill{} #1 Last checked #3%
}

@@

\newcommand{\numberOFruleINTERSECTIONS}[0]{%
    17,020%
}

@@
